Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-16 main.tex
add combined psf figures
Updates from Overleaf

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/psf_tests.pdf}
  \caption{\small{PSF tests.
  Each of the four panels labeled (a)--(d) shows a map view (Top Left) and cross section (Top Right) through a Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$\,,
  and a map view (Bottom Left) and cross section (Bottom Right) through the recovered perturbation, $\mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$.
  (a) 100~km diameter negative Gaussian anomaly at a depth of 300~km beneath Yellowstone.
  (b) 400~km diameter negative Gaussian anomaly at a depth of 2,000~km beneath Afar.
  (c) 300~km diameter negative Gaussian anomaly at a depth of 2,500~km beneath Easter Island.
  (d) 200~km diameter positive Gaussian anomaly at a depth of 900~km beneath Sumatra.
  }}
  \label{fig:psf_tests}
\end{figure}

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model Glad-M25,
including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.

@@

\begin{itemize}
\item[]{\it Afar} In Fig.~\ref{fig:plumes}(a),
we see that the Afar plume in model GLAD-M25 originates from the CMB, narrows its diameter
in the mid mantle, and broadens again above the 660~km discontinuity.
It exhibits
very similar behavior in TX2015 but differs significantly in SEMUCB-WM1.  
\item[]{\it Bermuda and Canary} In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 (i) the Farallon
slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMT and
rising all the way up the Earth's surface; (iv) the Afar hotspot from another angle.
\item[]{\it Cape Verde and Hoggar} Fig.~\ref{fig:plumes}(c) features (i) South America subduction; (ii) the Cape Verde hotspot extending from the CMB all the way to the surface; (iii) the Hoggar hotspot from 660~km to the surface. 
\item[]{\it Iceland and Eifel} Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
and ascends to the surface.
The intensification above 660~km may be an indication of partial melting.
\item[]{\it Easter and Galapagos} Fig.~\ref{fig:plumes}(e) contains (i) the Easter hotspot; (ii) the Galapagos
hotspot; (iii) the Central America slab.
In models GLAD-M25 and TX2015,
the Easter and Galapagos hotspots appear to originate from the same underlying plume in the deep mantle,
which is the eastern arm of the Pacific superplume.
\item[]{\it Marion and Kerguelen}
Finally,
in Fig.~\ref{fig:plumes}(f) we see the Marion and Kerguelen hotspots, which might be connected to Afar in the lower mantle.
Recovering these plumes is challenging due to poor data coverage in the southern hemisphere.
\end{itemize}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/psf/psf_tests.pdf}
  \caption{\small{PSF tests.
  Each of the four panels labeled (a)--(d) shows a map view (Top Left) and cross section (Top Right) through a Gaussian perturbation, $\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$\,,
  and a map view (Bottom Left) and cross section (Bottom Right) through the recovered perturbation, $\mathsf{H}\cdot\mathsf{\Delta}\mathsf{m}$\,, in~$\beta_\mathrm{V}$.
  (a) 100~km diameter negative Gaussian anomaly at a depth of 300~km beneath Yellowstone.
  (b) 400~km diameter negative Gaussian anomaly at a depth of 2,000~km beneath Afar.
  (c) 300~km diameter negative Gaussian anomaly at a depth of 2,500~km beneath Easter Island.
  (d) 200~km diameter positive Gaussian anomaly at a depth of 900~km beneath Sumatra.
  }}
  \label{fig:psf_tests}
\end{figure}

@@

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.

@@

\begin{itemize}
\item[]{\it Afar} In Fig.~\ref{fig:plumes}(a),
we see that the Afar plume in model GLAD-M25 originates from the CMB, narrows its diameter
in the mid mantle, and broadens again above the 660~km discontinuity.
It exhibits
very similar behavior in TX2015 but differs significantly in SEMUCB-WM1.  
\item[]{\it Bermuda and Canary} In Fig.~\ref{fig:plumes}(b), from left to right, we see in model GLAD-M25 (i) the Farallon
slab; (ii) the Bermuda hotspot above the 660~km discontinuity; (iii) the Canary hotspot originating from the CMB and
rising all the way up the Earth's surface; (iv) the Afar hotspot from another angle.
\item[]{\it Cape Verde and Hoggar} Fig.~\ref{fig:plumes}(c) features (i) South America subduction; (ii) the Cape Verde hotspot extending from the CMB all the way to the surface; (iii) the Hoggar hotspot from 660~km to the surface. 
\item[]{\it Iceland and Eifel} Fig.~\ref{fig:plumes}(d) shows a plume which rises from the CMB right below Iceland, reaches 660~km, amplifies,
and ascends to the surface.
The intensification above 660~km may be an indication of partial melting.
\item[]{\it Easter and Galapagos} Fig.~\ref{fig:plumes}(e) contains (i) the Easter hotspot; (ii) the Galapagos
hotspot; (iii) the Central America slab.
In models GLAD-M25 and TX2015,
the Easter and Galapagos hotspots appear to originate from the same underlying plume in the deep mantle,
which is the eastern arm of the Pacific superplume.
\item[]{\it Marion and Kerguelen}
Finally,
in Fig.~\ref{fig:plumes}(f) we see the Marion and Kerguelen hotspots, which might be connected to Afar in the lower mantle.
Recovering these plumes is challenging due to poor data coverage in the southern hemisphere.
\end{itemize}

### 2020-02-16 supplementary_material.tex
fix typos
Updates from Overleaf

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.pdf}
  \caption{\small{PSF test for the middle of the United States.
    A 160~km diameter negative Gaussian anomaly is placed at a depth of 500~km beneath the middle of the US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_mid}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}
